### 2016-07-20 lineups.Rnw
start on figure X

>>>>

\begin{figure}
<<results0b, fig.width=8, fig.height=3, out.width='\\linewidth', echo = FALSE, warning = FALSE>>=
load("Data/lus_ests_truth.rda")
lus_ests_truth$param_name <- 
  factor(lus_ests_truth$param_name,
    levels = c("rate", "outdegree (density)", "reciprocity",
               "transitive triplets jumping alcohol2",
               "number pairs at doubly achieved distance 2"))        
ggplot(data=lus_ests_truth) +
  geom_density(aes(x=param_est-true_value, fill=convergence), alpha= 0.6) +
  facet_grid(model+param_name~true_model, labeller="label_both") +
  theme_bw() +
  theme(legend.position="bottom") + 
  scale_colour_brewer("Convergence", palette="Set1") +
  xlab("Parameter Estimate") + xlim(c(-25,25))
@
\caption{\label{fig:convergence-ests}}
\end{figure}
